Proper radial distance as a coordinate in the Schwarzschild metric

### 2022-05-20 arxiv/template.tex
minor changes

\author{ \href{https://orcid.org/0000-0000-0000-0000}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Robin K. S. Hankin}\thanks{Use footnote for providing further
		information about author (webpage, alternative
		address)---\emph{not} for acknowledging funding agencies.} \\
              AUT University\\
              Auckland, New Zealand\\
	\texttt{hankin.robin@gmail.com} \\
}

@@

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={Proper radial distance as a coordinate in the Schwarzschild metric}
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={Robin K. S.~Hankin}
pdfkeywords={First keyword, Second keyword, More},
}

>>>>

\author{ \href{https://orcid.org/0000-0001-5982-0415}{\includegraphics[scale=0.06]{orcid.pdf}\hspace{1mm}Robin K. S. Hankin}\thanks{
\url{https://academics.aut.ac.nz/robin.hankin}}\\
              AUT University\\
              Auckland, New Zealand\\
	\texttt{hankin.robin@gmail.com} \\
}

@@

%%% Add PDF metadata to help others organize their library
%%% Once the PDF is generated, you can check the metadata with
%%% $ pdfinfo template.pdf
\hypersetup{
pdftitle={Proper radial distance as a coordinate in the Schwarzschild metric}
pdfsubject={q-bio.NC, q-bio.QM},
pdfauthor={Robin K. S.~Hankin}
pdfkeywords={Black holes, Schwarzschild metric, proper distance,
}
